---
title: "Water Stress in Mexico City"
author: "Mitsue Guerrero"
date: "10/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(janitor)
library(httr)
library(pageviews)
library(jsonlite)
library(gt)
library(sf)
```

# Project Domain: 
### Water stress in Mexico City

# Description:

<br>I will use 2019 data from the water department in Mexico City (SACMEX) to compare water consumption per neighborhoods (colonias) and which of these are at risk due to high precipitation. </br>

I will use the localization data (geographic coordinates) to join them.

# Source:
[Datos Abiertos Ciudad de Mexico](https://datos.cdmx.gob.mx/explore/dataset/consumo-agua/information/?location=10,19.35762,-99.14463&dataChart=eyJxdWVyaWVzIjpbeyJjaGFydHMiOlt7InR5cGUiOiJiYXIiLCJmdW5jIjoiQ09VTlQiLCJ5QXhpcyI6ImNvbnN1bW8iLCJzY2llbnRpZmljRGlzcGxheSI6dHJ1ZSwiY29sb3IiOiJyYW5nZS1CbHVlcyJ9XSwieEF4aXMiOiJhbGNhbGRpYSIsIm1heHBvaW50cyI6NTAsInNvcnQiOiIiLCJzZXJpZXNCcmVha2Rvd24iOiJpbmRpY2VfZGVzYXJyb2xsbyIsInN0YWNrZWQiOiJub3JtYWwiLCJjb25maWciOnsiZGF0YXNldCI6ImNvbnN1bW8tYWd1YSIsIm9wdGlvbnMiOnt9fX1dLCJ0aW1lc2NhbGUiOiIiLCJkaXNwbGF5TGVnZW5kIjp0cnVlLCJhbGlnbk1vbnRoIjp0cnVlfQ%3D%3D)

```{r Data Source 1 and 2 from CSV, message = FALSE}


data1_csv <- read_delim("raw-data/consumo-agua.csv", ";", locale = readr::locale(encoding = "UTF-8")) %>%
  clean_names()
consumo <- data1_csv %>% 
  select(consumo_total, nomgeo, indice_des) %>%
  group_by(nomgeo) %>% 
  summarise(consumo_avg = mean(consumo_total)) %>%
  arrange(desc(consumo_avg))

consumo$nomgeo <- factor(consumo$nomgeo, levels =consumo$nomgeo[order(consumo$consumo_avg)])

ggplot(consumo, aes(x = nomgeo, y = consumo_avg, fill = nomgeo, alpha = 0.5)) +
  theme_minimal() +
  geom_col() +
  coord_flip() +
  theme(legend.position = "none", panel.grid.major.y =  element_blank()) +
  ggtitle("Average water consumption by Municipality in Mexico City") +
  xlab("Municipality") + ylab ("Liters")





# gt(data1_csv) %>% tab_header(title = "Water Consumption in CDMX",
#                     subtitle = "2019 (Sample of 5)") 

# data2_csv <- read_delim("raw-data/atlas-de-riesgo-precipitacion.csv", ";", locale = readr::locale(encoding = "UTF-8")) %>% 
#   clean_names() %>% 
# 
# data2_csv
#gt(data2_csv) %>% tab_header(title = "Precipitation profile in CDMX",
                    #subtitle = "2019 (Sample of 5)") 
